 Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation

### 2021-06-03 analysis/paper/shceof.Rmd
Agrega extensión de series en métodos

@@

(ref:extended-series-cap) Time series extended using ERA5 back extended preliminary edition (period 1950 -- 1978) and ERA5 (period 1979 -- 2019). Each series is computed by projecting monthly geopotential height zonal anomalies standardised by level south of 20ºS onto the corresponding spatial pattern and scaled to zero mean and unit standard deviation. \textcolor{red}{Esta aclaración metodológica debería estar en la secció de métodos y revisa como expresas este caption para que sea consistente con el resto.}

>>>>

While we compute these complex pricipal components using data from 1979 to 2019, we extended the complex time series back to the 1950 -- 1978 period by projecting monthly geopotential height zonal anomalies standardised by level south of 20ºS onto the corresponding spatial patterns.

Each series is computed by projecting monthly geopotential height zonal anomalies standardised by level south of 20ºS onto the corresponding spatial pattern and scaled to zero mean and unit standard deviation.

@@

(ref:extended-series-cap) Time series extended using ERA5 back extended preliminary edition (period 1950 -- 1978) and ERA5 (period 1979 -- 2019).
Each series is scaled to zero mean and unit standard deviation.
